?????????????????

### 2022-11-18 article_1/article_1.tex
Export latex tables automatically from the Notebook

\setlength\parindent{24pt}
%\usepackage{float}
\usepackage{floatrow}
\usepackage{pdfpages}
\newsavebox\mysavebox
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\noindent{Classic techniques for obtaining paleomagnetic data, e.g., thermal demagnetization and alternating fields, are based on the progressive acquisition of the magnetization contained in cylindrical samples, usually of 10 cm$^3$. The magnetic signal of a single specimen is the result of the sum of moments contained in the assembly of ferromagnetic grains, including stable and unstable registers~\citep{DeGroot2021}. although there are recent well-structured studies of imaging magnetic minerals in thin-sections \citep[e.g.,][]{Almeida2014, Farchi2017,  Glenn2017, Lima2014, Lima2009, Nichols2016, Weiss2007, DeGroot2018, DeGroot2021}, obtaining NRM directions of individual grains in the rock fabric remains, to the best of our knowledge, a challenge deeply explored only by \cite{DeGroot2021}. With the possibility of isolating the individual contributions of a fairly large number ($10^6$ $>$ N $>$ $10^7$) of stable magnetic particles (SD/PSD) the magnetic directions recovered, using the average of their NRM vectors, would have an accurate paleomagnetic response \citep{Berndt2016}, however such number of observations is unfeasible for the currently insufficient measurements scales of the equipaments \citep{DeGroot2018}.}

@@

\noindent{Thus, $\bar{p}=\left[x_c\ \ y_c\ \ z_c\ \ b\right]^T$ will be the solution vector that satisfies Euler's Equation with the least possible error containing the position coordinates font center ($x_c$, $y_c$, $z_c$) and the base level (b).}

@@

\noindent{The magnetization is usually represented in spherical coordinates of intensity (Q (A/m)), declination (D (°)) and inclination (I (°)). Thus, the vector ${\bar{M}}_j$, containing the cartesian coordinates of magnetization, of the direct model can also be calculated as follows:}

\begin{equation} \label{eq:sphere7}
\small \left[\begin{matrix}{Mx}_j\\{My}_j\\{Mz}_j\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 1}}=Q_j\cdot\left[\begin{matrix}cos\left(I_j\right)\cdot c o s\left(D_j\right)\\cos\left(I_j\right)\cdot s i n\left(D_j\right)\\sin\left(I_j\right)\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 1}}  
\end{equation}

@@

@@

\noindent{In paleomagnetic studies the magnetization vectors are represented in terms of their declination (D) and inclination (I). These are given as a function of the magnetization vector ${\bar{h}}_j$ (\cref{eq:sphere8}) and represented in spherical coordinates (as shown in \cref{fig:VECTORS}).}

\begin{equation} \label{eq:sphere20}
\centering
\footnotesize \bar{\bar{Cov}} =\left[\begin{matrix}Var({mx}_1)&\cdots&\cdots&\cdots&\cdots&\cdots&\cdots\\\cdots&Var({my}_1)&\cdots&\cdots&\cdots&\cdots&\cdots\\\cdots&\cdots&Var({mz}_1)&\cdots&\cdots&\cdots&\cdots\\\cdots&\cdots&\cdots&\ddots&\cdots&\cdots&\cdots\\\cdots&\cdots&\cdots&\cdots&Var({mx}_L)&\cdots&\cdots\\\cdots&\cdots&\cdots&\cdots&\cdots&Var({my}_L)&\cdots\\\cdots&\cdots&\cdots&\cdots&\cdots&\cdots&Var({mz}_L)\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 3L}}\ 
\end{equation}

\begin{equation} \label{eq:sphere20}
\centering
\sigma_{{mx}_j}=\sqrt{Var({mx}_j)},\ \ \ \  \sigma_{{my}_j}=\sqrt{Var({my}_j)}\ \ \ \text{and}\ \ \ \  \sigma_{{mz}_j}=\sqrt{Var({mz}_j)}
\end{equation}

\noindent{Thus, the propagation of uncertainties of the declination ($D_j$), inclination ($I_j$) and magnetic moment ($m_j$) results are given as a function of the parameters obtained in \cref{eq:sphere20}:}

\begin{equation} \label{eq:sphere21}
\centering
\sigma_{D_j}=\sqrt{\left(\frac{\partial D_j}{\partial{mx}_j}\right)^2\cdot\ \left(\sigma_{{mx}_j}\right)^2+\left(\frac{\partial D_j}{\partial{my}_j}\right)^2\cdot\ \left(\sigma_{{my}_j}\right)^2}
\end{equation}

\begin{equation} \label{eq:sphere22}
\centering
\sigma_{I_j}=\sqrt{\left(\frac{\partial I_j}{\partial{mx}_j}\right)^2\cdot\ \left(\sigma_{{mx}_j}\right)^2+\left(\frac{\partial I_j}{\partial{my}_j}\right)^2\cdot\ \left(\sigma_{{my}_j}\right)^2+\left(\frac{\partial I_j}{\partial{mz}_j}\right)^2\cdot\ \left(\sigma_{{mz}_j}\right)^2}
\end{equation}

\begin{equation} \label{eq:sphere22_m}
\centering
\sigma_{m_j}=\sqrt{\left(\frac{\partial m_j}{\partial{mx}_j}\right)^2\cdot\ \left(\sigma_{{mx}_j}\right)^2+\left(\frac{\partial m_j}{\partial{my}_j}\right)^2\cdot\ \left(\sigma_{{my}_j}\right)^2+\left(\frac{\partial m_j}{\partial{mz}_j}\right)^2\cdot\ \left(\sigma_{{mz}_j}\right)^2}
\end{equation}

\noindent{Where:}

@@

\noindent{We applied the proposed method in a numerical simulation of a geological thin-section of dimensions 1000 μm x 1000 μm in a regular grid (1000 x 1000) for estimating the magnetization directions of four spherical sources uniformly magnetized (but different directions), according to \cref{tab:directmodel}. Totaling an observation number N = $10^6$ obtained at a sensor-sample distance of 5 μm and a spacing of 1 μm. Subsequently, a pseudorandom noise of normal Gaussian distribution, with a zero mean and standard variation ≅ 5\% of the anomaly amplitude, was added to the data as shown in Figure XX.}

% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
\begin{table}[htbp]
\caption{Initial position and magnetization parameters for each spherical source.}
\label{tab:directmodel}
\centering
\begin{tabular}[width=1.0\textwidth]{ccccccc}
\rowcolor[HTML]{E7E7E7} 
\cellcolor[HTML]{E7E7E7}                         & \multicolumn{3}{c}{\cellcolor[HTML]{E7E7E7}Center coordinates} & \multicolumn{3}{c}{\cellcolor[HTML]{E7E7E7}Magnetization} \\
\rowcolor[HTML]{E7E7E7} 
\multirow{-2}{*}{\cellcolor[HTML]{E7E7E7}Sphere} & X (µm)              & Y (µm)             & Z (µm)             & Q (A/m)            & D (°)            & I (°)            \\
1                                                & 250                 & 250                & 8.50               & 6.0                & -140             & -30              \\
\rowcolor[HTML]{E7E7E7} 
2                                                & 500                 & 500                & 10.0               & 6.0                & 0                & 62               \\
3                                                & 750                 & 750                & 5.30               & 6.0                & -70              & -50              \\
\rowcolor[HTML]{E7E7E7} 
4                                                & 200                 & 800                & 7.75               & 6.0                & 125              & 22              
\end{tabular}
\end{table}

\begin{table}[htbp]
\caption{Central positions of sources input vs Euler deconvolution solutions.}
\label{tab:eulerresults}
\centering
\begin{tabular}[width=1.0\textwidth]{ccccccc}
\rowcolor[HTML]{E7E7E7} 
\cellcolor[HTML]{E7E7E7}                         & \multicolumn{3}{c}{\cellcolor[HTML]{E7E7E7}Posição do Centro de   Entrada} & \multicolumn{3}{c}{\cellcolor[HTML]{E7E7E7}Solução de Euler} \\
\rowcolor[HTML]{E7E7E7} 
\multirow{-2}{*}{\cellcolor[HTML]{E7E7E7}Esfera} & X (µm)                  & Y (µm)                  & Z (µm)                 & X (µm)             & Y (µm)             & Z (µm)             \\
1                                                & 250                     & 250                     & 8.50                   & 249.144984         & 250.084691         & 8.17863468         \\
\rowcolor[HTML]{E7E7E7} 
2                                                & 500                     & 500                     & 10.0                   & 500.213134         & 500.443637         & 9.85904976         \\
3                                                & 750                     & 750                     & 5.30                   & 749.873747         & 750.127834         & 5.26685529         \\
\rowcolor[HTML]{E7E7E7} 
4                                                & 200                     & 800                     & 7.75                   & 200.177971         & 800.331017         & 7.82974687        
\end{tabular}
\end{table}

\begin{table}[htbp]
\caption{Input magnetization directions vs inversion solutions and their error propagation.}
\label{tab:inversionresults}
\centering
\begin{tabular}[width=1.0\textwidth]{ccccccc}
\rowcolor[HTML]{E7E7E7} 
\cellcolor[HTML]{E7E7E7}                         & \multicolumn{2}{c}{\cellcolor[HTML]{E7E7E7}Direção de Entrada} & \multicolumn{4}{c}{\cellcolor[HTML]{E7E7E7}Direções Recuperadas e   Incertezas} \\
\rowcolor[HTML]{E7E7E7} 
\multirow{-2}{*}{\cellcolor[HTML]{E7E7E7}Esfera} & D (°)                          & I (°)                         & D (°)               & $\sigma$ D (°)            & I (°)             & $\sigma$ I (°)           \\
1                                                & -140                           & -30                           & -137.0294           & ± 0.7641          & -32.6550          & ± 0.5169          \\
\rowcolor[HTML]{E7E7E7} 
2                                                & 0                              & 62                            & 2.5167              & ± 1.5004          & 60.5473           & ± 0.6917          \\
3                                                & -70                            & -50                           & -68.3316            & ± 0.6752          & -49.0172          & ± 0.3923          \\
\rowcolor[HTML]{E7E7E7} 
4                                                & 125                            & 22                            & 124.8320            & ± 0.6449          & 21.9940           & ± 0.4515         
\end{tabular}
\end{table}

\noindent{The test using a simply synthetic sample shows the great capability of the method by retrieving not only the precisely center positions }

\begin{singlespace}
\doublespacing
\bibliographystyle{agu}  % style file is seg.bst
\bibliography{article1}
\end{singlespace}
\end{document}

>>>>

\setlength\parindent{24pt}
%\usepackage{float}
\usepackage{floatrow}
\usepackage{pdfpages}
\newsavebox\mysavebox

\usepackage{booktabs} % to import tables directly from python
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\noindent{Classic techniques for obtaining paleomagnetic data, e.g., thermal demagnetization and alternating fields, are based on the progressive acquisition of the magnetization contained in cylindrical samples, usually of 10 cm$^3$. The magnetic signal of a single specimen is the result of the sum of moments contained in the assembly of ferromagnetic grains, including stable and unstable registers~\citep{DeGroot2021}. Although there are recent well-structured studies of imaging magnetic minerals in thin-sections \citep[e.g.,][]{Almeida2014, Farchi2017,  Glenn2017, Lima2014, Lima2009, Nichols2016, Weiss2007, DeGroot2018, DeGroot2021}, obtaining NRM directions of individual grains in the rock fabric remains, to the best of our knowledge, a challenge deeply explored only by \cite{DeGroot2021}. With the possibility of isolating the individual contributions of a fairly large number ($10^6$ $>$ N $>$ $10^7$) of stable magnetic particles (SD/PSD) the magnetic directions recovered, using the average of their NRM vectors, would have an accurate paleomagnetic response \citep{Berndt2016}, however such number of observations is unfeasible for the currently insufficient measurements scales of the equipaments \citep{DeGroot2018}.}

@@

\noindent{Thus, $\bar{p}=\left[x_c\ \ y_c\ \ z_c\ \ b\right]^T$ will be the solution vector that satisfies Euler's Equation with the least possible error containing the position coordinates source center ($x_c$, $y_c$, $z_c$) and the base level (b).}

@@

\noindent{The magnetization is usually represented in spherical coordinates of intensity (M (A/m)), declination (D (°)) and inclination (I (°)). Thus, the vector ${\bar{M}}_j$, containing the cartesian coordinates of magnetization, of the direct model can also be calculated as follows:}

\begin{equation} \label{eq:sphere7}
\small \left[\begin{matrix}{Mx}_j\\{My}_j\\{Mz}_j\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 1}}=M_j\cdot\left[\begin{matrix}cos\left(I_j\right)\cdot c o s\left(D_j\right)\\cos\left(I_j\right)\cdot s i n\left(D_j\right)\\sin\left(I_j\right)\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 1}}  
\end{equation}

@@

\noindent{In paleomagnetic studies the magnetization vectors are represented in terms of their declination (D) and inclination (I). These are given as a function of the magnetization vector ${\bar{m}}_j$ (\cref{eq:sphere8}) and represented in spherical coordinates (as shown in \cref{fig:VECTORS}).}

\begin{equation} \label{eq:sphere20}
\centering
\small \bar{\bar{Cov}}= \left[~ \text{\emph{diag}}\left(\begin{matrix}{\sigma_{{mx}_1}}^2&{\sigma_{{my}_1}}^2&{\sigma_{{mz}_1}}^2&\cdots&{\sigma_{{mz}_L}}^2\end{matrix}\right) \right]_{\text{\tiny 3L $\times$ 3L}}\
\end{equation}

\begin{equation} \label{eq:sphere20}
\centering
\sigma_{{mx}_j}=\sqrt{{\sigma_{{mx}_j}}^2},\ \ \ \  \sigma_{{my}_j}=\sqrt{{\sigma_{{my}_j}}^2}\ \ \ \text{and}\ \ \ \  \sigma_{{mz}_j}=\sqrt{{\sigma_{{mz}_j}}^2}
\end{equation}

\noindent{Thus, the propagation of uncertainties of the declination ($D_j$), inclination ($I_j$) and magnetic moment ($m_j$) results are given as a function of the parameters (detailed in Appendix A.2) obtained in \cref{eq:sphere20}:}

\begin{equation} \label{eq:sphere21}
\centering
\small \sigma_{D_j}=\sqrt{\left(\frac{\partial D_j}{\partial{mx}_j}\right)^2\cdot\ \left(\sigma_{{mx}_j}\right)^2+\left(\frac{\partial D_j}{\partial{my}_j}\right)^2\cdot\ \left(\sigma_{{my}_j}\right)^2}
\end{equation}

\begin{equation} \label{eq:sphere22}
\centering
\small \sigma_{I_j}=\sqrt{\left(\frac{\partial I_j}{\partial{mx}_j}\right)^2\cdot\ \left(\sigma_{{mx}_j}\right)^2+\left(\frac{\partial I_j}{\partial{my}_j}\right)^2\cdot\ \left(\sigma_{{my}_j}\right)^2+\left(\frac{\partial I_j}{\partial{mz}_j}\right)^2\cdot\ \left(\sigma_{{mz}_j}\right)^2}
\end{equation}

\begin{equation} \label{eq:sphere22_m}
\centering
\small \sigma_{m_j}=\sqrt{\left(\frac{\partial m_j}{\partial{mx}_j}\right)^2\cdot\ \left(\sigma_{{mx}_j}\right)^2+\left(\frac{\partial m_j}{\partial{my}_j}\right)^2\cdot\ \left(\sigma_{{my}_j}\right)^2+\left(\frac{\partial m_j}{\partial{mz}_j}\right)^2\cdot\ \left(\sigma_{{mz}_j}\right)^2}
\end{equation}

\noindent{We applied the proposed method in a numerical simulation of a geological thin-section of dimensions 1000 μm x 1000 μm in a regular grid (1000 x 1000) for estimating the magnetization directions of four spherical sources uniformly magnetized (but with different directions), according to \cref{tab:ModelTab}. Totaling an observation number N = $10^6$ obtained at a sensor-sample distance of 5 μm and a grid spacing of 1 μm. Subsequently, the data vector was contaminated with a pseudo-random noise of normal Gaussian distribution with a zero mean and 25 nT standard deviation, as shown in \cref{fig:SimpleSynthetic}a.}

\begin{figure}[htbp]
\centering
\includegraphics[width=1.0\textwidth]{SimpleSynthetic.png}
\caption{blablabla.}
\label{fig:SimpleSynthetic}
\end{figure}

% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
\input{input_par_table}

% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
\input{solution_par_table}

\noindent{The test using a simply synthetic sample shows the great capability of the method by retrieving not only the precisely center positions \ref{AppendixA.1} }

\begin{singlespace}
\doublespacing
\bibliographystyle{agu}  % style file is seg.bst
\bibliography{article1}
\end{singlespace}

\section{Appendix A}
\subsection{Appendix A.1} \label{AppendixA.1}

@@

\subsection{Appendix A.2} \label{AppendixA.2}

@@

\end{document}
